### 2014-09-03 tex/proofs.tex
Added more detail to the Field Write proof, and fixed some typos in the lazy Field Access rule.

To see that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, we must consider how $s_s^\prime$ is constructed. Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\ell^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_s(\cfgnt{R}_s(h(l_\ell),f))$, and let $\theta^\prime =   \cfgnt{L}_s^\prime(\cfgnt{R}_s^\prime(h(l_\ell),f))$. If $l_\beta \neq l_\ell$, then either $\theta = \theta^\prime$ or $\theta \neq \theta^\prime$ . In the first case, we are guaranteed that the homomorphism works by default. Otherwise, if $\theta \neq \theta^\prime$.  We can see from the construction of the set $X$ in the summary Field Write rule that any feasible location in the set $\theta$ must also be in the set $\theta^\prime$. Since $s_\ell \sqsubset s_s$, we know that $h(l_\alpha)$ is in $\theta$, and is likewise in $\theta^\prime$. We have now established that in either case:
 $$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$$
On the other hand, if $l_\beta = l_\ell$, then we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\ell,f ))$. From the lazy field rule, we can use the fact that $ $ surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}( )$, and since $s_\ell \sqsubset s_s$, we know $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r}_x)$ for some constraint $phi_b$. Using this fact, we can apply the summary Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(adfa)$

@@

@@

Next, we show that every state represented by $s_s^\prime$ is in the feasible set. We use the same argument as in the field read proof, that because $s_s^\prime$ represents every state in the feasible set, and since the cardinality of the set of states represented by $s_s^\prime$ is less than or equal to the cardinality of the feasible set, that $s_s^\prime$ can only represent feasible states.

>>>>

To see that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, we must consider how $s_s^\prime$ is constructed. Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\ell^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_s(\cfgnt{R}_s(h(l_\ell),f))$, and let $\theta^\prime =   \cfgnt{L}_s^\prime(\cfgnt{R}_s^\prime(h(l_\ell),f))$.

Suppose $l_\beta \neq l_\ell$. In this case either $\theta = \theta^\prime$ or $\theta \neq \theta^\prime$ . In the first case, we are guaranteed that the homomorphism works by default. Otherwise, if $\theta \neq \theta^\prime$.  We can see from the construction of the set $X$ in the summary Field Write rule that any feasible location in the set $\theta$ must also be in the set $\theta^\prime$. Since $s_\ell \sqsubset s_s$, we know that $h(l_\alpha)$ is in $\theta$, and is likewise in $\theta^\prime$. We have now established that in either case where $l_\beta \neq l_\ell$, $(\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$.

On the other hand, suppose $l_\beta = l_\ell$. In this case we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\ell,f ))$. From the lazy field rule, we can surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}(\cfgnt{r} )$, and since $s_\ell \sqsubset s_s$, we know that$(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r})$ for some constraint $\phi_b$. Using this fact, we can apply the summary Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_c\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}^\prime(l_\ell,f))$

@@

Establishing the fact that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$ is left as an exercise to the reader.

@@

To show that $s_s^\prime$ is exact with respect to the feasible set, we use the same argument as in the field read proof: that because $s_s^\prime$ represents every state in the feasible set, and since the cardinality of the set of states represented by $s_s^\prime$ is less than or equal to the cardinality of the feasible set, that $s_s^\prime$ can only represent feasible states.
